\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2020-07-10 submission/manuscript.Rmd
Metagenomic part in M&M done.

# Selection of groups for plotting
plot <- filter(community, taxlevel==2 |
                 (taxlevel==4 & str_detect(taxon, "^Chloroplast$")) |
                 (taxlevel==3 & str_detect(rankID, filter(community, str_detect(taxon, "^Proteobacteria$"))[[2]]))) %>%
  filter_at(6:ncol(.), any_vars(. >= 1)) %>%
  mutate_at(5:ncol(.), list(~case_when(taxon=="Cyanobacteria" ~ . - .[taxon=="Chloroplast"], TRUE ~ .))) %>%
  mutate_at(5:ncol(.), list(~case_when(taxon=="Proteobacteria" ~ . - sum(.[taxlevel==3 & str_detect(rankID, filter(community, str_detect(taxon, "^Proteobacteria$"))[[2]])]), TRUE ~ .))) %>%
  mutate(taxon=str_replace(taxon, "Proteobacteria", "Other Proteobacteria")) %>%
  mutate(taxon=str_replace_all(taxon, c("unknown_unclassified"="No_Relative", "unknown"="No_Relative"))) %>%
  filter_at(6:ncol(.), any_vars(. >= 1)) %>%
  bind_rows(summarise_all(., list(~ifelse(is.numeric(.), 100-sum(.), paste("Other"))))) %>%
  rename_at(names(metadata), ~unname(metadata)) %>%
  arrange(taxon %in% "No_Relative") %>%
  mutate(mean=rowMeans(select(., contains(c("SCy", "FCyM", "FCaM", "FCa"))), na.rm=TRUE)) %>%
  mutate(sd=rowSds(as.matrix(select(., contains(c("SCy", "FCyM", "FCaM", "FCa")))), na.rm=TRUE)) %>%
  arrange(desc(mean))
```

@@

# Calculating relative abundaces
community <- group_by(community, taxlevel) %>%
  mutate_at(5:ncol(.), list(~. / sum(.) * 100)) %>%
  ungroup()

@@

# Selection of groups for plotting
chloroplast <- filter(community, taxlevel==5) %>%
  rename_at(names(metadata), ~unname(metadata)) %>%
  mutate(mean=rowMeans(select(., contains(c("SCy", "FCyM", "FCaM", "FCa"))), na.rm=TRUE)) %>%
  mutate(sd=rowSds(as.matrix(select(., contains(c("SCy", "FCyM", "FCaM", "FCa")))), na.rm=TRUE)) %>%
  arrange(desc(mean))
```

@@

### Sequence analysis
```{r}
# Calculation of the error rate based on the ATCC MSA-1002 mock community
error <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.error.summary", na="") %>%
  filter(numparents==1) %>%
  mutate(mismatches_weight=weight*mismatches) %>%
  mutate(total_weight=weight*total)
error <- sum(error$mismatches_weight)/sum(error$total_weight)*100
# Calculation of the number of sequences in the negative control
nc <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.nr_v138.wang.tax.summary") %>%
  filter(taxon=="Root") %>%
  select(NC_1)
```
Obtained sequences were analyzed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0) [@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommendations given from the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 138; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Sequences classified as chloroplasts by SILVA were exported and reclassifed using mothur and the RDP (http://rdp.cme.msu.edu/) training set (version 16) reference files adapted for mothur [@Cole2014]. In comparison to SILVA, RDP allows a more detailed classification of chloroplast sequences. Pipeline data processing and visualization was done using R (version 3.6.0) [@RCoreTeam2019],  package tidyverse (version 1.3.0) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019; @Xie2020; @Allaire2019; @Xie2018; @Zhu2019; @Neuwirth2014; @Bengtsson2020]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (https://github.com/mkorlevic/Korlevic_SelectiveRemoval_EnvironMicrobiol_2020). Based on the ATCC MSA-1002 mock community included in the analysis a sequencing error rate of `r error` \si{\percent} was determined, which is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative control processed together with the samples yielded only `r nc` sequences after sequence quality curation.

>>>>

# Selection of groups for plotting
plot <- filter(community, taxlevel==2 |
                 (taxlevel==4 & str_detect(taxon, "^Chloroplast$")) |
                 (taxlevel==3 & str_detect(rankID, filter(community, str_detect(taxon, "^Proteobacteria$"))[[2]]))) %>%
  filter_at(6:ncol(.), any_vars(. >= 1)) %>%
  mutate_at(5:ncol(.), list(~case_when(taxon=="Cyanobacteria" ~ . - .[taxon=="Chloroplast"], TRUE ~ .))) %>%
  mutate_at(5:ncol(.), list(~case_when(taxon=="Proteobacteria" ~ . - sum(.[taxlevel==3 & str_detect(rankID, filter(community, str_detect(taxon, "^Proteobacteria$"))[[2]])]), TRUE ~ .))) %>%
  mutate(taxon=str_replace(taxon, "Proteobacteria", "Other Proteobacteria")) %>%
  mutate(taxon=str_replace_all(taxon, c("unknown_unclassified"="No_Relative", "unknown"="No_Relative"))) %>%
  filter_at(6:ncol(.), any_vars(. >= 1)) %>%
  bind_rows(summarise_all(., list(~ifelse(is.numeric(.), 100-sum(.), paste("Other"))))) %>%
  rename_at(names(metadata), ~unname(metadata)) %>%
  arrange(taxon %in% "No_Relative") %>%
  mutate(mean=rowMeans(select(., contains("SCy"), contains("FCyM"), contains("FCaM"), contains("FCa")), na.rm=TRUE)) %>%
  mutate(sd=rowSds(as.matrix(select(., contains("SCy"), contains("FCyM"), contains("FCaM"), contains("FCa"))), na.rm=TRUE)) %>%
  arrange(desc(mean))
```

@@

# Calculating relative abundances
community <- group_by(community, taxlevel) %>%
  mutate_at(5:ncol(.), list(~. / sum(.) * 100)) %>%
  ungroup()

@@

# Selection of groups for plotting
chloroplast <- filter(community, taxlevel==5) %>%
  rename_at(names(metadata), ~unname(metadata)) %>%
  mutate(mean=rowMeans(select(., contains("SCy"), contains("FCyM"), contains("FCaM"), contains("FCa")), na.rm=TRUE)) %>%
  mutate(sd=rowSds(as.matrix(select(., contains("SCy"), contains("FCyM"), contains("FCaM"), contains("FCa"))), na.rm=TRUE)) %>%
  arrange(desc(mean))
```

@@

```{r}
# Calculation of the error rate based on the ATCC MSA-1002 mock community
error <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.error.summary", na="") %>%
  filter(numparents==1) %>%
  mutate(mismatches_weight=weight*mismatches) %>%
  mutate(total_weight=weight*total)
error <- sum(error$mismatches_weight)/sum(error$total_weight)*100
# Calculation of the number of sequences in the negative control
nc <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.nr_v138.wang.tax.summary") %>%
  filter(taxon=="Root") %>%
  select(NC_1)
```
Obtained sequences were analyzed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0) [@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommendations given from the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 138; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Sequences classified as chloroplasts by SILVA were exported and reclassifed using mothur and the RDP (http://rdp.cme.msu.edu/) training set (version 16) reference files adapted for mothur [@Cole2014]. In comparison to SILVA, RDP allows a more detailed classification of chloroplast sequences. Pipeline data processing and visualization was done using R (version 3.6.0) [@RCoreTeam2019],  package tidyverse (version 1.3.0) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019; @Xie2020; @Allaire2019; @Xie2018; @Zhu2019; @Neuwirth2014; @Bengtsson2020]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (https://github.com/mkorlevic/Korlevic_SelectiveRemoval_EnvironMicrobiol_2020). Based on the ATCC MSA-1002 mock community included in the analysis a sequencing error rate of `r error` \si{\percent} was determined, which is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative control processed together with the samples yielded only `r nc` sequences after sequence quality curation.

### Metagenomics
Four samples were selected and sent on dry ice to IMGM Laboratories, Martinsried, Germany for metagenomic sequencing. DNA was purified using AMPure XP Beads (Beckman Coulter, USA) applying a bead:DNA ratio of 1:1 (v/v), quantified with a Qubit dsDNA HS Assay Kit (Thermo Fisher Scientific, USA) and check for integrity on a 1 \si{\percent} agarose gel. Metagenomic sequencing libraries were generated from 300 \si{\ng} of input DNA using a NEBNext Ultra II FS DNA Library Prep Kit for Illumina (New England Biolabs, USA) according to the manufacturer's instructions. Fragments were selected (500 -- 700 bp) using AMPure XP Beads, PCR enriched for 3 -- 5 cycles and quality controlled. Libraries generated from different DNA samples were pooled and sequenced on an Illumina NovaSeq 6000 sequencing system (2 × 250 bp).

Obtained sequences were assembled individually using MEGAHIT (version  1.1.2) [@Li2015] under default settings. Putative genes were predicted from contings longer than 200 bp using Prodigal (version  2.6.3) [@Hyatt2010] in metagenome mode (-p meta). Abundances of predicted genes were expressed as Reads Per Kilobase Million (RPKM) and calculated using the BWA algorithm (version  0.7.16a) [@Li2009a]. All predicted genes were functionally annotated using the eggNOG-mapper [@Huerta-Cepas2017] and eggNOG database (version 5.0) [@Huerta-Cepas2019]. The taxonomic classification of sequences was determined using the lowest common ancestor algorithm adapted from DIAMOND (version 0.8.36) [@Buchfink2015] and by searching against the non-redundant database (NR). To determine phylogeny the top 10 \si{\percent} hits with an e-value < 1 × 10^-5^ were used (\-\-top 10).

### 2020-07-10 submission/manuscript.tex
Metagenomic part in M&M done.

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Selective DNA and Protein Isolation from Marine Macrophyte Surfaces},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{\textbf{Selective DNA and Protein Isolation from Marine Macrophyte
Surfaces}}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\usepackage{times} % Times New Roman font
\usepackage[T1]{fontenc}

@@

@@

\hypertarget{sequence-analysis}{%
\subsubsection{Sequence analysis}\label{sequence-analysis}}

Obtained sequences were analyzed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0) (Schloss \emph{et al.}, 2009) according to the MiSeq
Standard Operating Procedure (MiSeq SOP;
\url{https://mothur.org/wiki/MiSeq_SOP}) (Kozich \emph{et al.}, 2013)
and recommendations given from the Riffomonas project to enhance data
reproducibility (\url{http://www.riffomonas.org/}). For alignment and
classification of sequences the SILVA SSU Ref NR 99 database (release
138; \url{http://www.arb-silva.de}) was used (Quast \emph{et al.}, 2013;
Yilmaz \emph{et al.}, 2014). Sequences classified as chloroplasts by
SILVA were exported and reclassifed using mothur and the RDP
(\url{http://rdp.cme.msu.edu/}) training set (version 16) reference
files adapted for mothur (Cole \emph{et al.}, 2014). In comparison to
SILVA, RDP allows a more detailed classification of chloroplast
sequences. Pipeline data processing and visualization was done using R
(version 3.6.0) (R Core Team, 2019), package tidyverse (version 1.3.0)
(Wickham \emph{et al.}, 2019) and multiple other packages (Xie, 2014,
2015, 2019b, 2019a, 2020; Neuwirth, 2014; Xie \emph{et al.}, 2018;
Allaire \emph{et al.}, 2019; Zhu, 2019; Bengtsson, 2020). The detailed
analysis procedure including the R Markdown file for this paper are
available as a GitHub repository
(\url{https://github.com/mkorlevic/Korlevic_SelectiveRemoval_EnvironMicrobiol_2020}).
Based on the ATCC MSA-1002 mock community included in the analysis a
sequencing error rate of 0.009 \si{\percent} was determined, which is in
line with previously reported values for next-generation sequencing data
(Kozich \emph{et al.}, 2013; Schloss \emph{et al.}, 2016). In addition,
the negative control processed together with the samples yielded only 2
sequences after sequence quality curation.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Allaire2019}{}%
Allaire, J.J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
A., et al. (2019) Rmarkdown: Dynamic documents for R.

@@

@@

@@

@@

@@

\leavevmode\hypertarget{ref-RCoreTeam2019}{}%
R Core Team (2019) A language and environment for statistical computing,
Vienna, Austria: R Foundation for Statistical Computing.

@@

\leavevmode\hypertarget{ref-Xie2014}{}%
Xie, Y. (2014) Knitr: A comprehensive tool for reproducible research in
R. In \emph{Implementing Reproducible Computational Research}. Stodden,
V., Leisch, F., and Peng, R.D. (eds). New York: Chapman and Hall/CRC,
pp. 3--32.

\leavevmode\hypertarget{ref-Xie2019}{}%
Xie, Y. (2019a) Knitr: A general-purpose package for dynamic report
generation in R.

@@

\leavevmode\hypertarget{ref-Xie2020}{}%
Xie, Y. (2020) TinyTex: Helper functions to install and maintain 'TeX
Live', and compile 'LaTeX' documents.

@@

\leavevmode\hypertarget{ref-Zhu2019}{}%
Zhu, H. (2019) KableExtra: Construct complex table with 'kable' and pipe
syntax.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Selective DNA and Protein Isolation from Marine Macrophyte Surfaces},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{times} % Times New Roman font
\usepackage[T1]{fontenc}

@@

\title{\textbf{Selective DNA and Protein Isolation from Marine Macrophyte
Surfaces}}
\author{}
\date{\vspace{-2.5em}}

@@

Obtained sequences were analyzed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0) (Schloss \emph{et al.}, 2009) according to the MiSeq
Standard Operating Procedure (MiSeq SOP;
\url{https://mothur.org/wiki/MiSeq_SOP}) (Kozich \emph{et al.}, 2013)
and recommendations given from the Riffomonas project to enhance data
reproducibility (\url{http://www.riffomonas.org/}). For alignment and
classification of sequences the SILVA SSU Ref NR 99 database (release
138; \url{http://www.arb-silva.de}) was used (Quast \emph{et al.}, 2013;
Yilmaz \emph{et al.}, 2014). Sequences classified as chloroplasts by
SILVA were exported and reclassifed using mothur and the RDP
(\url{http://rdp.cme.msu.edu/}) training set (version 16) reference
files adapted for mothur (Cole \emph{et al.}, 2014). In comparison to
SILVA, RDP allows a more detailed classification of chloroplast
sequences. Pipeline data processing and visualization was done using R
(version 3.6.0) (R Core Team, 2019), package tidyverse (version 1.3.0)
(Wickham \emph{et al.}, 2019) and multiple other packages (Xie, 2014,
2015, 2020; Neuwirth, 2014; Xie \emph{et al.}, 2018; Y. Xie, 2019b,
2019a; Allaire \emph{et al.}, 2019; Zhu, 2019; Bengtsson, 2020). The
detailed analysis procedure including the R Markdown file for this paper
are available as a GitHub repository
(\url{https://github.com/mkorlevic/Korlevic_SelectiveRemoval_EnvironMicrobiol_2020}).
Based on the ATCC MSA-1002 mock community included in the analysis a
sequencing error rate of 0.009 \si{\percent} was determined, which is in
line with previously reported values for next-generation sequencing data
(Kozich \emph{et al.}, 2013; Schloss \emph{et al.}, 2016). In addition,
the negative control processed together with the samples yielded only 2
sequences after sequence quality curation.

\hypertarget{metagenomics}{%
\subsubsection{Metagenomics}\label{metagenomics}}

Four samples were selected and sent on dry ice to IMGM Laboratories,
Martinsried, Germany for metagenomic sequencing. DNA was purified using
AMPure XP Beads (Beckman Coulter, USA) applying a bead:DNA ratio of 1:1
(v/v), quantified with a Qubit dsDNA HS Assay Kit (Thermo Fisher
Scientific, USA) and check for integrity on a 1 \si{\percent} agarose
gel. Metagenomic sequencing libraries were generated from 300 \si{\ng}
of input DNA using a NEBNext Ultra II FS DNA Library Prep Kit for
Illumina (New England Biolabs, USA) according to the manufacturer's
instructions. Fragments were selected (500 -- 700 bp) using AMPure XP
Beads, PCR enriched for 3 -- 5 cycles and quality controlled. Libraries
generated from different DNA samples were pooled and sequenced on an
Illumina NovaSeq 6000 sequencing system (2 × 250 bp).

Obtained sequences were assembled individually using MEGAHIT (version
1.1.2) (Li \emph{et al.}, 2015) under default settings. Putative genes
were predicted from contings longer than 200 bp using Prodigal (version
2.6.3) (Hyatt \emph{et al.}, 2010) in metagenome mode (-p meta).
Abundances of predicted genes were expressed as Reads Per Kilobase
Million (RPKM) and calculated using the BWA algorithm (version 0.7.16a)
(Li and Durbin, 2009). All predicted genes were functionally annotated
using the eggNOG-mapper (Huerta-Cepas \emph{et al.}, 2017) and eggNOG
database (version 5.0) (Huerta-Cepas \emph{et al.}, 2019). The taxonomic
classification of sequences was determined using the lowest common
ancestor algorithm adapted from DIAMOND (version 0.8.36) (Buchfink
\emph{et al.}, 2015) and by searching against the non-redundant database
(NR). To determine phylogeny the top 10 \si{\percent} hits with an
e-value \textless{} 1 × 10\textsuperscript{-5} were used (-\/-top 10).

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Allaire2019}{}%
Allaire, J.J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
A., et al. (2019) rmarkdown: Dynamic documents for R.

@@

\leavevmode\hypertarget{ref-Buchfink2015}{}%
Buchfink, B., Xie, C., and Huson, D.H. (2015) Fast and sensitive protein
alignment using DIAMOND. \emph{Nat Methods} \textbf{12}: 59--60.

@@

\leavevmode\hypertarget{ref-Huerta-Cepas2017}{}%
Huerta-Cepas, J., Forslund, K., Coelho, L.P., Szklarczyk, D., Jensen,
L.J., von Mering, C., and Bork, P. (2017) Fast genome-wide functional
annotation through orthology assignment by eggNOG-mapper. \emph{Mol Biol
Evol} \textbf{34}: 2115--2122.

\leavevmode\hypertarget{ref-Huerta-Cepas2019}{}%
Huerta-Cepas, J., Szklarczyk, D., Heller, D., Hernández-Plaza, A.,
Forslund, S.K., Cook, H., et al. (2019) eggNOG 5.0: A hierarchical,
functionally and phylogenetically annotated orthology resource based on
5090 organisms and 2502 viruses. \emph{Nucleic Acids Res} \textbf{47}:
D309--D314.

@@

\leavevmode\hypertarget{ref-Hyatt2010}{}%
Hyatt, D., Chen, G.-L., LoCascio, P.F., Land, M.L., Larimer, F.W., and
Hauser, L.J. (2010) Prodigal: Prokaryotic gene recognition and
translation initiation site identification. \emph{BMC Bioinformatics}
\textbf{11}: 119.

@@

\leavevmode\hypertarget{ref-Li2015}{}%
Li, D., Liu, C.-M., Luo, R., Sadakane, K., and Lam, T.-W. (2015)
MEGAHIT: An ultra-fast single-node solution for large and complex
metagenomics assembly via succinct de Bruijn graph.
\emph{Bioinformatics} \textbf{31}: 1674--1676.

\leavevmode\hypertarget{ref-Li2009a}{}%
Li, H. and Durbin, R. (2009) Fast and accurate short read alignment with
BurrowsWheeler transform. \emph{Bioinformatics} \textbf{25}: 1754--1760.

@@

\leavevmode\hypertarget{ref-RCoreTeam2019}{}%
R Core Team (2019) R: A language and environment for statistical
computing, Vienna, Austria: R Foundation for Statistical Computing.

@@

\leavevmode\hypertarget{ref-Xie2014}{}%
Xie, Y. (2014) knitr: A comprehensive tool for reproducible research in
R. In \emph{Implementing Reproducible Computational Research}. Stodden,
V., Leisch, F., and Peng, R.D. (eds). New York: Chapman and Hall/CRC,
pp. 3--32.

\leavevmode\hypertarget{ref-Xie2019}{}%
Xie, Y. (2019a) knitr: A general-purpose package for dynamic report
generation in R.

@@

\leavevmode\hypertarget{ref-Xie2020}{}%
Xie, Y. (2020) tinytex: Helper functions to install and maintain 'TeX
Live', and compile 'LaTeX' documents.

@@

\leavevmode\hypertarget{ref-Zhu2019}{}%
Zhu, H. (2019) kableExtra: Construct complex table with 'kable' and pipe
syntax.
